% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.2 (16/9/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% TODO:
% 1. Integrate biber/bibtex for article citation under publications.
% 2. Figure out a smoother way for the document to flow onto the next page.
% 3. Add styling information for a "Projects/Hacks" section.
% 4. Add location/address information
% 5. Merge OpenFont and MacFonts as a single sty with options.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
% v1.1:
% 1. Fixed several compilation bugs with \renewcommand
% 2. Got Open-source fonts (Windows/Linux support)
% 3. Added Last Updated
% 4. Move Title styling into .sty
% 5. Commented .sty file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\documentclass[]{deedy-resume-openfont}
\usepackage{fancyhdr}
 
\pagestyle{fancy}
\fancyhf{}
 
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{}{Pranjul Agarwal}{ \urlstyle{same}\href{https://pranjulagarwal.github.io/}{pranjulagarwal.github.io}| \href{https://www.facebook.com/pranjul.agarwal.129}{fb.co/pranjul}\\
\href{mailto:pranjul.agarwal1999@gmail.com}{pranjul.agarwal1999@gmail.com} | +91-9897287436 | \href{mailto:pranjul.ecebt18@nituk.ac.in}{pranjul.ecebt18@nituk.ac.in}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 

\subsection{NIT UTTARAKHAND}
\descript{B.Tech in Electronics}
\location{2018 - Present | UK, India}
College of Engineering \\
\location{ Cum. GPA : 7.01 / 10.0 }
\sectionsep

\subsection{St. John's School}
\location{Grad. May 2017 |  Roorkee, India}
\location{XII   : 85/100}
\location{X     : 9.8/10}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Links} 
LinkedIn    ://  \href{https://www.linkedin.com/in/pranjul-agarwal-2000/}{\bf PranjulAgarwal} \\
Github      :// \href{https://github.com/PranjulAgarwal}{\bf PranjulAgarwal} \\
Facebook    :// \href{https://www.facebook.com/pranjul.agarwal.129}{\bf pranjul.agarwal} \\
Twitter     ://  \href{https://twitter.com/PranjulAgarwal6}{\bf @PranjulAgarwal6} \\
Portfolio   ://  \href{https://pranjulagarwal.github.io/}{\bf pranjulagarwal} \\


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{Programming}
\location{Over 30000 lines:}
Java \textbullet{}   C \textbullet{} Express \textbullet{} Javascript \\
HTML-CSS \textbullet{} React.Js \textbullet{} Node.Js \textbullet{} MongoDb \\ 
\location{Over 10000 lines:}
Python \textbullet{} Vue.js \textbullet{} MySQL \textbullet{} Android \\
\location{Familiar:}
AWS \textbullet{} Flutter \textbullet{} Git \textbullet{} Django 
\sectionsep


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Coursework}

\subsection{Undergraduate}
Operating Systems \\
Artificial Intelligence \\
Competitive Programming \\
JAVA Programming \\
Database Management \\
Object Oriented Methodology \\
Data Structure and Algorithms \\


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}
\runsubsection{Shopify Partners}
\descript{| Software Development Engineer }
\location{Feb 2021 - May 2021 | Remote}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item My task was to build interactive consumer data from multiple systems and RESTfully abstract to the UI through a Node.js backend.
\item Build the end user web apps for Shopify clients (Small and Medium Sized Businesses). 
\item Full-stack developer - Wrote and reviewed code for JS using React, MongoDb, Node.Js and AWS 
\end{tightemize}
\sectionsep

\runsubsection{Indian 0}
\descript{| Full Stack Developer }
\location{May 2020 – Jun 2020 | Remote}
\begin{tightemize}
\item Worked with the Web Developer team, in Javascript and HTML-CSS to plan, to design and develop the Digital Portfolios for the customers of Indian0 (A digital portfolio management)
\item Created a HTML and JS framework for the Portfolio Structure.
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     PROJECTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Projects}
\runsubsection {\href{https://redditflaird.herokuapp.com/}{Reddit - Flair Detector}}
\descript{| Web App}
\location{Aug 2020 – Nov 2020 }
A Web App for Detecting Flairs in Reddit posts. Done data aquisition of reddit posts from the r/india subreddit, perform classification of the posts into 4 different flairs, later deployed the best model as a web app by utilising ML and NLP algorithms.
\sectionsep

\runsubsection {\href{https://play.google.com/store/apps/details?id=app.develepor.shivam.grocit}{Grocit}}
\descript{| Online Grocery Shopping | Android Application}
\location{Apr 2020 – May 2020 | Roorkee, UK}
An android application for grocery deliveries. Made this application for local grocery store enabling to grow its business online and enabling easy deliveries for customers. Available on PlayStore. 
\sectionsep

\runsubsection {\href{https://trailerflix-netflix-clone.netlify.app/}{TrailerFLix}}
\descript{| Web App | Netflix Clone}
\location{May 2021 – May 2021 }
 It is a React based web-app, a clone of Netflix style. It shows latest trending movies and shows with their trailer, also recommends you top shows and movies categorised in different genres using TMDB API.
\sectionsep

\runsubsection {\href{https://codeeditor-codepen-clone.netlify.app/}{CodeEditor}}
\descript{| Web App | CodePen Clone}
\location{May 2021 – May 2021 }
 Online code-editor is a tool that resides on a remote server and is accessible via browsers.
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     AWARDS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Awards} 
\begin{tabular}{rll}
2020	     & Nationwide top 20        & Flipakrt GRiD2.0, Hackathon\\
2019	     & Leadership               & A.B.V.P. All India Inter NIT-Summit\\
2017	     & 1\textsuperscript{st}    & Excellent Academics Performance, Intermediate\\
2015	     & 1\textsuperscript{st}    & Excellent Academics Performance, Matriculation\\
2014	     & 5\textsuperscript{th}    & Indian School Olympiad, India\\
\end{tabular}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     PUBLICATIONS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Publications} 
\renewcommand\refname{\vskip -1.5em} % Couldn't get this working from the .cls file
\bibliographystyle{abbrv}
P. Goel, R. Behl, P. Agarwal and S. Gupta. Face Identification System, Conference: 2019, International Conference on Issues and Challenges in Intelligent Computing Techniques (ICICT).
\nocite{*}


\end{minipage} 
\end{document}  \documentclass[]{article}
